High angular resolution dust density and temperature maps from \Herschel\ imaging data

### 2012-08-05 documents/herschel_dust.tex
bibliography replacement

The hyperparameters $\alpha$---parameters of the priors---set the
strictness or information content of the priors.  We want to give
these hyperparameters values that have been dervied objectively from
the data, so that the collection of \emph{all} data informs the prior
probability for the parameters $\Omega_k, T_k, \beta_k$ affecting any
small part of the data.  The best methods for such hyperparameter
inference is hierarchical Bayesian inference, which is too
computationally costly for the present effort.  The approximation to
hierarchical inference adopted here is that of leave-some-out
cross-validation: We drop randomly chosen small subsets of the data,
perform the inference of the dust-map parameters $\Omega_k, T_k,
\beta_k$ using the remaining (the non-left-out) data, predict the
left-out data, and base the hyperparameter settings on the quality of
the predictions.

@@

\begin{thebibliography}{70}
\bibitem[Bendinelli(1991)]{bendinelli}
Bendinelli,~O., 1991, \apj, 366, 599
\bibitem[Bendinelli \& Parmeggiani(1995)]{bendinelli2}
Bendinelli,~O. \& Parmeggiani,~G., 1995, \aj, 109, 572
\bibitem[Bovy \etal(2011a)]{xd}
Bovy,~J., Hogg,~D.~W., \& Roweis,~S., 2011, Ann. Appl. Stat., 5, 1657
\bibitem[Bovy \etal(2011b)]{xdqso}
Bovy,~J., \etal, 2011, \apj, 729, 141
\bibitem[Bovy \etal(2012)]{xdqsoz}
Bovy,~J. \etal, 2012, \aj, 749, 41
\bibitem[Cappellari(2002)]{cappellari}
Cappellari,~M., 2002, \mnras, 333, 400
\bibitem[Ciotti \& Bertin(1999)]{ciotti}
Ciotti,~L. \& Bertin,~G., 1999, \aa, 352, 447
\bibitem[Emsellem \etal(1994)]{emsellem}
Emsellem,~E., Monnet,~G., Bacon,~R., \& Nieto,~J.-L., 1994, \aap, 285, 739
\bibitem[Peng \etal(2002)]{galfit}
Peng,~C.~Y., Ho, L.~C., Impey,~C.~D., \& Rix,~H.-W., 2002, \aj, 124, 266
\end{thebibliography}

>>>>

The hyperparameters $\alpha$---parameters of the priors---set the
strictness or information content of the priors.  We want to give
these hyperparameters values that have been dervied objectively from
the data, so that the collection of \emph{all} data informs the prior
probability for the parameters $\Omega_k, T_k, \beta_k$ affecting any
small part of the data.  The best methods for such hyperparameter
inference is hierarchical Bayesian inference (for example,
\citealt{eccentricity}, MORE REFERENCES), which is too computationally
costly for the present effort.  The approximation to hierarchical
inference adopted here is that of leave-some-out cross-validation: We
drop randomly chosen small subsets of the data, perform the inference
of the dust-map parameters $\Omega_k, T_k, \beta_k$ using the
remaining (the non-left-out) data, predict the left-out data, and base
the hyperparameter settings on the quality of the predictions.

@@

\begin{thebibliography}{70}
\bibitem[Hogg \etal(2010)]{eccentricity}
Hogg,~D.~W., Myers,~A.~D., \& Bovy,~J., 2010, \apj, 725, 2166
\end{thebibliography}
